\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-17 chapters/5_experiments_cityscapes.tex
Add comparison details to suppl.
Add more details about CS exps

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}. See Appendix \ref{sec:cityscapes_appendix} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 in \cite{liu2018affinity}.

% \begin{table}
%     \centering
%     \begin{subtable}[t!]{0.5\textwidth}\centering
%         \begin{tabular}{c|| c| c| c |c }
%         & \multicolumn{4}{c}{\thead{Add Cannot-Link-Constraints:}} \\
%         & \multicolumn{2}{c}{\thead{\textsc{No}}} & \multicolumn{2}{c}{\thead{\textsc{Yes}}} \\
%          & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
% Sum & 0.55  & {\color{Orange} 0.313 } & 0.55  & {\color{Orange} 0.319 } \\\midrule
% Abs. Max. & 0.45  & {\color{Orange} 0.321 } & & \\\midrule
% \textbf{Mean}& \textbf{0.35 } & {\color{ForestGreen} \textbf{0.343} } & 0.25  & {\color{Orange} 0.339 } \\\midrule

% Max & 0.85 & {\color{Red} 0.243 } & 0.50  & {\color{Orange} 0.325 } \\\midrule
% Min & 0.50  & {\color{Red} 0.000 } & 0.50  & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.341 } & - & - \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
%     \label{tab:results_cityscapes}
% \end{table}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c| c | c}
%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
%     \label{tab:linkage-criteria}
% \end{table*}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. For our experiments, we used the state-of-the-art proposal-free pipeline proposed in \cite{liu2018affinity} (GMIS) that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was publicly available, so we simply replaced their final graph-merging algorithm (GMIS-Agglo) with \algname{}. See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. GMIS-Agglo requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

### 2019-05-17 chapters/5_experiments_noise.tex
Add more details about CS exps

\subsection{Results}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}. Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}. This simple method also achieved remarkably superior scores to other state-of-the-art multi-step methods. \TODO{Wait for new test-scores}
In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework. In Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all scores linkage tested with \algname{} on the full CREMI training data.

@@

\UPDATE{Plots in Fig. \ref{fig:noise_plots} summarize 6000 experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph\footnote{We tested 20 values of noise and, for each setup, we averaged the scores over 30 runs.}. In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version. 
Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections. Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence. The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.   
The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. Nevertheless, in more challenging parts of the data (see Fig. \ref{fig:cremi_comparison}) or in the presence of noise, it often incorrectly merge regions together, leading to more unbalanced graph partitioning. In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.  }
\begin{figure}[b]
\centering
\begin{minipage}[T]{0.54\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|l|cc}
           & \algname{}  &  \multicolumn{2}{c}{Use constraints:} \\
           & Linkage & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{Average}& \textbf{34.3}  & 33.9  \\
 & GMIS-Agglo \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
\multirow{2}{*}{GMIS Pipeline} & Max &   24.3  &   32.5  \\
 & Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 & Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.43\textwidth}
    \centering
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

>>>>

\subsection{Results}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\TODO{Mention Appendix} The difficulty of the dataset is highlighted by the poor scores achieved by THRESH in Table \ref{tab:results_cremi_train}. Among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}. This simple method also achieved remarkably superior scores to other state-of-the-art multi-step methods. \TODO{Wait for new test-scores}
In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of the different agglomerative algorithms included in our framework. In Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all scores linkage tested with \algname{} on the full CREMI training data.

@@

\UPDATE{Plots in Fig. \ref{fig:noise_plots} summarize 6000 experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph\footnote{We tested 20 values of noise and, for each setup, we averaged the scores over 30 runs.}. In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version. 
Our findings confirm that \algname{} with \emph{Average} linkage criterion represents the most robust algorithm tested and that is the one benefiting more from additional long-range edge connections. Other versions using cannot-link constraints generally lead to an over-segmentation, but are robust to ``leaks through holes'' given by missing boundary evidence. The greedy \emph{absolute maximum} linkage proposed by \cite{wolf2018mutex} is the least robust to noise, but, as we show in Table \ref{tab:full_cremi_results}, it represents an efficient and considerably faster option.   
The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. Nevertheless, in more challenging parts of the data (see Fig. \ref{fig:cremi_comparison}) or in the presence of noise, it often incorrectly merge regions together, leading to more unbalanced graph partitioning. In these cases, the use of cannot-link constraints or a more robust average linkage are preferable.  }
\begin{figure}[b]
\centering
\begin{minipage}[T]{0.59\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
 & MultiStepHAC \cite{liu2018affinity} & \UPDATE{33.0} & -  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

### 2019-05-17 chapters/supplementary.tex
Add more details about CS exps

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
% \tilde{F}(x;\theta)=\begin{cases}
% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
% \end{cases}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}). \TODO{Add more details}

@@

\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
Mention the main trick in the loss: ignore background pixels (so focus on boundaries). Same mapping defined in \ref{eq:mappings}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c| c | c | c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
% sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
% mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
% sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
% MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
% sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
% mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
% mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
% max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
% max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
% min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
% min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
%     \label{tab:results_cremi_crop_C}
% \end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c| c | c | c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
% mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
% MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
% max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
% mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
% sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
% sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
% sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
% sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
% mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
% min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
% min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
% max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
%     \label{tab:results_cremi_crop_C}
% \end{table*}

% \begin{table}
%     \centering
%     \begin{subtable}[t!]{0.5\textwidth}\centering
%         \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
%         \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
%     \label{tab:results_cityscapes_full}
% \end{table}

% \begin{algorithm}[t]
%   \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
%    \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
%   \hspace*{\algorithmicindent} 
%   \begin{algorithmic}[1]

%       \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
%       \State Init. \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
%       \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
%       \State
%       \While{PQ is \textbf{not} empty}
%         \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
%         \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
%           \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
%           \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
%             % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
%             \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
%           \EndFor
%         \EndIf
%         \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
%           \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
%         \EndIf
%       \EndWhile
%       \State
%       \Return $\Pi$
%   \end{algorithmic}
%   \label{main_alg_suppl}
% \end{algorithm}

>>>>

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source version of simplex noise \cite{perlin2001noise}, which is an improved open-source version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
% \tilde{F}(x;\theta)=\begin{cases}
% F(x;\theta)+\mathcal{K}\cdot\max\left(N(x),0\right) & \text{if merge-biased}\\
% F(x;\theta)+\mathcal{K}\cdot\min\left(N(x),0\right) & \text{if split-biased}
% \end{cases}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a merge-biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a split-biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}). \TODO{Add impl. details}

@@

\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model. In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (GMIS-Agglo): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; a new HAC problem including long-range affinities is then initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.

Since GMIS-Agglo is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach. We added two 1x1 convolutional layers to the instance-branch model and trained them by using a

% Mention the main trick in the loss: ignore background pixels (so focus on boundaries).

% Same mapping defined in \ref{eq:mappings}

% Due to the unbalanced nature of the original affinities, we had to perform a parameter-search of the $\beta$ hyper-parameter. Since with a certain value of $\beta$ could be optimal for some versions of \algname{} but not others, we decide to perform a parameter search for each version of \algname{} and Table \ref{tab:results_cityscapes_val} lists the best-case performances for each of the methods.
